Model_CFU

### 2017-01-06 code/HumanCdGF_cdiff_colonization.Rmd
nmds on day 0 comm for colonization level

>>>>

### Regression cannot be used to predict colonization levels in this dataset

Since the % Variation explained by the RF model decreases to ~0% when removing the extreme values, the suggests that we do not have the data to make accurate predictions of the colonization level due to the low number of samples at the extremes. However we do seem to have a separation between the high and low but we cannot model the middle levels with linear regression. So another way we could look at this would to classify the groups.

##### NMDS of colonization level

```{r NMDS, eval = F}
#export shared file to generate theta-yc distances in mothur
#read in full shared file
full_shared_file <- 'data/process/full_shared.shared'
full_shared_file <- read.table(full_shared_file, sep = '\t', header = T)

nmds_df <- colonized_cfu %>% 
    select(mouse_id, human_source, log_cfu_med) %>% 
    right_join(shared_day_0) %>% 
    filter(!is.na(log_cfu_med))
nmds_df <- data.frame(colonization_level= ifelse(nmds_df$log_cfu_med >= 8.25, 'hi',
                                     ifelse(nmds_df$log_cfu_med <= 6.5, 'lo', 'mid')),
                       select(nmds_df, -log_cfu_med))
nmds_shared <- full_shared_file[full_shared_file$Group %in% 
                                  paste0(gsub('_','-',nmds_df$mouse_id),'-D0'),]
write.table(nmds_shared, file= '~/Desktop/day_0_communities.shared', sep = '\t', 
            row.names = F, quote = F)
nmds_CL_design <- data.frame(paste0(gsub('_','-',nmds_df$mouse_id),'-D0'), nmds_df$colonization_level)
write.table(nmds_CL_design, file= '~/Desktop/day_0_communities.CL.design', sep = '\t', 
      col.names = F, row.names = F, quote = F)
nmds_src_design <- data.frame(paste0(gsub('_','-',nmds_df$mouse_id),'-D0'), nmds_df$human_source)
write.table(nmds_src_design, file= '~/Desktop/day_0_communities.SRC.design', sep = '\t', 
      col.names = F, row.names = F, quote = F)
#min(apply(nmds_shared[,-c(1:3)],1,sum)) # 2423
#run dist command in mothur
#dist.shared(shared=~/Desktop/day_0_communities.shared, calc=thetayc, subsample=2400)
#nmds(phylip=~/Desktop/day_0_communities.thetayc.0.03.lt.ave.dist)
Number of dimensions:	2
Lowest stress :	0.297773
R-squared for configuration:	0.55791
#nmds(phylip=~/Desktop/day_0_communities.thetayc.0.03.lt.ave.dist, mindim=3, maxdim=3)
Number of dimensions:	3
Lowest stress :	0.191484
R-squared for configuration:	0.71623
#amova(phylip=~/Desktop/day_0_communities.thetayc.0.03.lt.ave.dist, design=~/Desktop/day_0_communities.CL.design)
hi-lo-mid	Among	Within	Total
SS	4.48543	8.08716	12.5726
df	2	30	32
MS	2.24272	0.269572

Fs:	8.31955
p-value: <0.001*

hi-lo	Among	Within	Total
SS	2.4372	0.676826	3.11403
df	1	10	11
MS	2.4372	0.0676826

Fs:	36.0093
p-value: <0.001*

hi-mid	Among	Within	Total
SS	2.08215	7.41077	9.49293
df	1	23	24
MS	2.08215	0.322207

Fs:	6.46215
p-value: <0.001*

lo-mid	Among	Within	Total
SS	2.30066	8.08673	10.3874
df	1	27	28
MS	2.30066	0.299508

Fs:	7.68145
p-value: <0.001*
#significantly different centroids

#homova(phylip=~/Desktop/day_0_communities.thetayc.0.03.lt.ave.dist, design=~/Desktop/day_0_communities.CL.design)
HOMOVA	BValue	P-value	SSwithin/(Ni-1)_values
hi-lo-mid	21.6225	<0.001*	0.000145266	0.0966271	0.370517
hi-lo	14.1638	<0.001*	0.000145266	0.0966271
hi-mid	18.2515	<0.001*	0.000145266	0.370517
lo-mid	3.48295	<0.001*	0.0966271	0.370517
# all groups have significantly different variation (hi = 0.0001, mid = 0.37, lo = 0.097)

dist_cl <- vegdist(nmds_df[,-c(1,2)])
nmds <- metaMDS(nmds_df[,-c(1:2)])
stressplot(nmds, dist_cl)
plot(nmds, type = 'n')
points(nmds, display = 'sites', pch = 21, bg = as.numeric(as.factor(nmds_df$human_source)))
#text(nmds, display = 'species', cex = 0.5)
envfit(nmds ~ )
```

#### Classification of Colonization Level

```{r classify colonization level}

#### Features driving classification

```{r features of col level}

While these features seem to drive the grouping, it still needs to be further validated/investigated to see if these results repeat in similar microbiomes since the high and low are largely homogenous communities and the middle group is made of heterogenous commnunities.
